---
title: "Project 1"
output: flexdashboard::flex_dashboard
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(tidyverse)
library(flexdashboard)


#####  Question 1 a
df1a_raw = read_rds("YL_Q1a.rds") %>% as.tibble()
df1a = df1a_raw %>% mutate(method=as.factor(method))

sv = df1a %>% pull(sampleSize) %>% unique()
delta = df1a %>% pull(type) %>% unique()

df1a_sort = df1a %>% group_by(sampleSize,method,trueValue) %>% arrange(desc(confiUpper)) %>% mutate(sortID = 1:n()) %>% ungroup()

#####  Question 1 b

df1b_raw = read_rds("YL_Q1b.rds") %>% as.tibble()
df1b = df1b_raw %>% mutate(method=as.factor(method))
df1b_sort = df1b %>% group_by(sampleSize,method,trueValue) %>% arrange(desc(confiUpper)) %>% mutate(sortID = 1:n()) %>% ungroup()

##### Question 2


df2raw = read_rds("YL_Q2.rds") %>% as.tibble()

# assign ID for plotting
df2 = df2raw %>% mutate(method=as.factor(method))

qv2 = df2 %>% pull(mixRatio) %>% unique() %>% as.numeric()
tv2 = df2 %>% pull(trueValue) %>% unique()
sv2 = df2 %>% pull(sampleSize) %>% unique()

# ggplot(df %>% filter(sampleSize==500,trueValue==0.2),aes(x=ID)) + 
#   geom_segment(aes(x=ID,y=confiLower,xend=ID,yend=confiUpper),color='orange1') +
#   geom_hline(yintercept = 0.2)


df2_sort = df2 %>% group_by(mixRatio,sampleSize,method,trueValue) %>% arrange(desc(confiUpper)) %>% mutate(sortID = 1:n()) %>% ungroup()



```

# Question 1a

Column {.sidebar}
--------------------------------------------------


```{r}
sliderInput('sampleSize', h3('Sample Size'), min=sv[1], max=max(sv),
            value=sv[1], step=500, round=0)

selectInput(
  "delta", label = h3("Delta (pair diff):"),
  choices = delta, selected = delta[1]
)
```

Population proportions: 

```{r}
renderTable({
  tibble(p=paste0("p",1:3),value=c(0.5,0.3,0.2))
})

```

Pair difference:

```{r}
renderTable({
  tibble(delta=delta,value=c(0.2,0.3,0.1))
})

```


Outputs
-----------------------------------------------------------------------


### Confidence Intervals {data-height=100}
* __Large sample sizes help to narrow the confidence intervals for both method__
* __Interval length from Method 1 varies for different delta, while Method 2 is fixed__
    + p1-p2: method 1 is wider; p2-p3: method 2 is wider;
    
### Confidence Intervals

```{r}
dataset <- reactive({
  df1a_sort %>% filter(sampleSize==input$sampleSize,type==input$delta)
})

tvalue <- reactive({
  df1a_sort %>% filter(type==input$delta) %>% pull(trueValue) %>% unique()
})
renderPlot({
  
  p = ggplot(dataset(),aes(x=sortID)) +
      geom_ribbon(aes(ymin= confiLower,ymax = confiUpper,fill=method),alpha=0.5)+
      geom_hline(yintercept = tvalue(),size=1,color="dodgerblue4") + 
      scale_y_continuous(breaks=seq(-0.25,0.65,0.1),limits=c(-0.25, 0.65)) + 
      theme_minimal() + theme(legend.position = 'right')
  
  print(p)
})
```


# Question 1b


Column {.sidebar}
--------------------------------------------------


```{r}
sliderInput('sampleSize1b', h3('Sample Size'), min=sv[1], max=max(sv),
            value=sv[1], step=500, round=0)

selectInput(
  "delta1b", label = h3("Delta (pair diff):"),
  choices = delta, selected = delta[1]
)
```

Population proportions: 

```{r}
renderTable({
  tibble(p=paste0("p",1:3),value=c(0.5,0.48,0.02))
})

```

Pair difference:

```{r}
renderTable({
  tibble(delta=delta,value=c(0.02,0.48,0.46))
})

```


Outputs
-----------------------------------------------------------------------

### Observations: {data-height=100}
* __Large sample sizes help to narrow the confidence intervals for both method__
* __Interval length from Method 1 varies for different delta, while Method 2 is fixed__
    + p1-p2: method 1 is wider; p2-p3: method 2 is wider;

### Confidence Intervals

```{r}
dataset1b <- reactive({
  df1b_sort %>% filter(sampleSize==input$sampleSize1b,type==input$delta1b)
})

tvalue1b <- reactive({
  df1b_sort %>% filter(type==input$delta1b) %>% pull(trueValue) %>% unique()
})

renderPlot({
  p = ggplot(dataset1b(),aes(x=sortID)) +
      geom_ribbon(aes(ymin= confiLower,ymax = confiUpper,fill=method),alpha=0.5)+
      geom_hline(yintercept = tvalue1b(),size=1,color="dodgerblue4") +
      scale_y_continuous(breaks=seq(-0.25,0.65,0.1),limits=c(-0.25, 0.65)) +
      theme_minimal() + theme(legend.position = 'right')
  
  print(p)
})
```


# Question 2


Column {.sidebar}
--------------------------------------------------


```{r}
sliderInput('sampleSize2', h3('Sample Size'), min=sv2[1], max=max(sv2),
            value=sv2[1], step=500, round=0)

selectInput(
  "delta2", label = h3("Delta (pair diff):"),
  choices = delta, selected = delta[1]
)

sliderInput("mixRatio",h3("Mix ratio"),min=min(qv2),max=max(qv2),
            value = qv2[1], step=0.1, round=0)

```

Population proportions: 

```{r}
renderTable({
  tibble(p=paste0("p",1:3),value1=c(0.46,0.44,0.10),
         r=paste0("r",1:3),value2 = c(0.34,0.33,0.33))
})

```

Pair difference:

```{r}
renderTable({
  tibble(delta=delta,value=c(0.02,0.36,0.34))
})

```


Outputs
-----------------------------------------------------------------------


### Additional Observations: {data-height=90}
* __Generally Increasing mix ratio moves the confidence interval away from "originals value".__    
* __But it may still cover individual "original value", if the pair difference doesn't change too much after contamination.__

### Confidence Intervals


```{r}
dataset2 <- reactive({
  df2_sort %>% filter(sampleSize==input$sampleSize2,type==input$delta2,mixRatio==input$mixRatio)
})

tvalue2 <- reactive({
  df2_sort %>% filter(type==input$delta2) %>% pull(trueValue) %>% unique()
})

renderPlot({
  p2 = ggplot(dataset2(),aes(x=sortID)) +
      geom_ribbon(aes(ymin= confiLower,ymax = confiUpper,fill=method),alpha=0.5)+
      geom_hline(yintercept = tvalue2(),size=1,color="dodgerblue4") +
      scale_y_continuous(breaks=seq(-0.25,0.65,0.1),limits=c(-0.25, 0.65)) +
      theme_minimal() + theme(legend.position = 'right')
  
  print(p2)
})
```


